### 2022-03-21 paper/localpsf.tex
remove scaled impulse response widehat variable

We compute impulse responses $\impulseresponse_{x_i}$ in batches by applying $\Aop$ to Dirac combs. The Dirac comb, $\diraccomb_k$, associated with a batch of sample points, $\pointbatch_k$, is the following weighted sum of Dirac distributions (point sources) centered at the points $x_i \in \pointbatch_k$:
\begin{equation*}
	\diraccomb_k := \sum_{x_i \in \pointbatch_k} \delta_{x_i} / V(x_i).
\end{equation*}
We compute the \emph{impulse response batch}, $\eta_k$, by applying $\Aop$ to the Dirac comb:
\begin{equation}
	\label{eq:dirac_comb_H_action}
	\combresponse_k := \left(\Aop \diraccomb_k^*\right)^*
	=\sum_{x_i \in \pointbatch_k} \widehat{\impulseresponse}_{x_i}.
\end{equation}
The last equality in \eqref{eq:dirac_comb_H_action} follows from linearity and the definition of $\widehat{\impulseresponse}_{x_i}$ in \eqref{eq:scaled_impulse_response} and \eqref{eq:impulse_response_delta_action}.
%\begin{equation}
%\label{eq:phi_b}
%\combresponse_k = \sum_{x_i \in \pointbatch_k} \impulseresponse_{x_i} / V(x_i).
%\end{equation}
%\begin{equation}
%	\label{eq:phi_b}
%	\combresponse_k = \left(\Aop \left(\sum_{x_i \in \pointbatch_k} \delta_{x_i}/V(x_i)\right)^*\right)^* = \sum_{x_i \in \pointbatch_k} \left(\Aop \delta_{x_i}^*\right)^* / V(x_i) = \sum_{x_i \in \pointbatch_k} \impulseresponse_{x_i} / V(x_i).
%\end{equation}
Since the points $x_i$ are chosen so that the ellipsoid $E_{x_i}$ that (approximately) supports $\impulseresponse_i$, and the ellipsoid $E_{x_j}$ that (approximately) supports $\impulseresponse_j$ do not overlap when $i \neq j$, we have (approximately)
\begin{equation}
\label{eq:varphi_eval}
	\impulseresponse_{x_i}(z) / V(x_i) = \widehat{\impulseresponse}_{x_i}(z) =
	\begin{cases}
		\combresponse_k(z), & z \in E_{x_i} \\
		0, & \text{otherwise}
	\end{cases}
\end{equation}
for all $x_i \in \pointbatch_k$. By performing one matrix-vector product, $\xi_k \mapsto \left(\Aop \diraccomb_k^*\right)^*$, we recover the impulse responses $\impulseresponse_{x_i}$ associated with every point $x_i \in \pointbatch_k$.

>>>>

We compute impulse responses $\impulseresponse_{x_i}$ in batches by applying $\Aop$ to Dirac combs. The Dirac comb, $\diraccomb_k$, associated with a batch of sample points, $\pointbatch_k$, is the following weighted sum of Dirac distributions (point sources) centered at the points $x_i \in \pointbatch_k$:
\begin{equation*}
	\diraccomb_k := \sum_{x_i \in \pointbatch_k} \delta_{x_i} / V(x_i).
\end{equation*}
We compute the \emph{impulse response batch}, $\eta_k$, by applying $\Aop$ to the Dirac comb:
\begin{equation}
	\label{eq:dirac_comb_H_action}
	\combresponse_k := \left(\Aop \diraccomb_k^*\right)^*
	=\sum_{x_i \in \pointbatch_k} \impulseresponse_{x_i} / V(x_i).
\end{equation}
The last equality in \eqref{eq:dirac_comb_H_action} follows from linearity and the definition of $\impulseresponse_{x_i}$ in \eqref{eq:impulse_response_delta_action}.
%\begin{equation}
%\label{eq:phi_b}
%\combresponse_k = \sum_{x_i \in \pointbatch_k} \impulseresponse_{x_i} / V(x_i).
%\end{equation}
%\begin{equation}
%	\label{eq:phi_b}
%	\combresponse_k = \left(\Aop \left(\sum_{x_i \in \pointbatch_k} \delta_{x_i}/V(x_i)\right)^*\right)^* = \sum_{x_i \in \pointbatch_k} \left(\Aop \delta_{x_i}^*\right)^* / V(x_i) = \sum_{x_i \in \pointbatch_k} \impulseresponse_{x_i} / V(x_i).
%\end{equation}
Since the points $x_i$ are chosen so that the ellipsoid $E_{x_i}$ that (approximately) supports $\impulseresponse_i$, and the ellipsoid $E_{x_j}$ that (approximately) supports $\impulseresponse_j$ do not overlap when $i \neq j$, we have (approximately)
\begin{equation}
\label{eq:varphi_eval}
	\impulseresponse_{x_i}(z) =
	\begin{cases}
		\combresponse_k(z) V(x_i), & z \in E_{x_i} \\
		0, & \text{otherwise}
	\end{cases}
\end{equation}
for all $x_i \in \pointbatch_k$. By performing one matrix-vector product, $\xi_k \mapsto \left(\Aop \diraccomb_k^*\right)^*$, we recover the impulse responses $\impulseresponse_{x_i}$ associated with every point $x_i \in \pointbatch_k$.
